Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-04-22 presentation/presentation.tex
ppt update logo
ppt minor update

% Inbuilt themes in beamer
\documentclass{beamer}

% Theme choice:
\usetheme{Antibes}
\usecolortheme{beaver}

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro–Adaptive Control 
} 
\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, \and Kyunghwan Choi\inst{1}}
\date{\today}

@@

\logo{
    \includegraphics[height=1cm]{../template/figs/logo_GIST.png}
}

@@

% Remove logo from the next slides
\logo{}

@@

% Lists frame
\section{Lists in Beamer}
\begin{frame}{Lists in Beamer}

This is an unordered list:
\begin{itemize}
    \item Item 1
    \item Item 2
    \item Item 3
\end{itemize}

and this is an ordered list:
\begin{enumerate}
    \item Item 1
    \item Item 2
    \item Item 3
\end{enumerate}

@@

% Blocks frame
\section{Blocks in Beamer}
\begin{frame}{Blocks in Beamer}
    \begin{block}{Standard Block}
        This is a standard block.
    \end{block}
    \begin{alertblock}{Alert Message}
        This block presents alert message.
    \end{alertblock}
    \begin{exampleblock}{An example of typesetting tool}
        Example: MS Word, \LaTeX{}
    \end{exampleblock}
\end{frame}

>>>>

% Inbuilt themes in beamer
\documentclass[aspectratio=169]{beamer}

% Theme choice:
\usetheme{Antibes}
% \usecolortheme{beaver}

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro–Adaptive Control 
} 
\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}}
\date{\today}

@@

\logo{
    \includegraphics[height=0.4cm]{logo_KAIST.png}
    \hspace{.5cm}%
    \includegraphics[height=0.4cm]{logo_KAIST.png}
}

\AtBeginSection[]{%
  \frame<beamer>{ 
    \frametitle{Outline}   
    \tableofcontents[currentsection] 
  }
}

@@

@@

% Lists frame
\section{Background and Contributions}

\subsection{Introduction to Neuro–Adaptive Control}

\begin{frame}{Introduction to Neuro–Adaptive Control}

    \begin{block}{Standard Block}
        This is a standard block.
    \end{block}
    \begin{alertblock}{Alert Message}
        This block presents alert message.
    \end{alertblock}
    \begin{exampleblock}{An example of typesetting tool}
        Example: MS Word, \LaTeX{}
    \end{exampleblock}

@@

\subsection{Limitations of Neuro–Adaptive Control}

\begin{frame}

\section{Proposed Method}
\subsection{Weight Norm Constraint}
\begin{frame}{Weight Norm Constraint}
    \begin{block}{Weight Norm Constraint}
        \begin{itemize}
            \item This is a list item.
            \item This is another list item.
        \end{itemize}
    \end{block}
\end{frame}

\section{Numerical Validation}

\subsection{Simulation Setup}
\begin{frame}{Weight Norm Constraint}
    \begin{block}{Weight Norm Constraint}
        \begin{itemize}
            \item This is a list item.
            \item This is another list item.
        \end{itemize}
    \end{block}
\end{frame}

\subsection{Simulation Results}
\begin{frame}{Weight Norm Constraint}
    \begin{block}{Weight Norm Constraint}
        \begin{itemize}
            \item This is a list item.
            \item This is another list item.
        \end{itemize}
    \end{block}
\end{frame}

\section{Conclusion}

\subsection{Conclusion and Future Work}
\begin{frame}{Conclusion}
    \begin{block}{Weight Norm Constraint}
        \begin{itemize}
            \item This is a list item.
            \item This is another list item.
        \end{itemize}
    \end{block}
\end{frame}

\section{}
\begin{frame}{}
    \centering \Large
    \emph{Thank you for your attention!}
\end{frame}
